Modelling potential environmental impacts of science activity in Antarctica

### 2025-09-24 talk/index.qmd
added north arrow joke...
more fiddling around

##
![](fig-study-area-1.png){fig-align="center"}

@@

get_graph_plot <- function(G, main, crs = 2193) {
  return(ggplot() +
    geom_sf(data = G |> 
              get_graph_as_line_layer(crs = 2193), lwd = 0.35, colour = "white") +
    geom_sf(data = G |> 
              vertex_attr() |> as.data.frame() |> st_as_sf(coords = 1:2, crs = crs), 
            size = 8, fill = "black", colour = "white", shape = 21, lwd = 1) +
    coord_sf(xlim = c(-270, 270) + 1e6, 
             ylim = c(-270, 270) + 1e6, expand = FALSE) +
    ggtitle(main)) +
    theme(
      plot.background = element_rect(fill = "black"),
    )
}

@@

hex_grid_pts <- grid_pts |>
  st_bbox() |> 
  st_make_grid(square = FALSE, what = "centers", cellsize = 107.457) |>
  st_as_sf() |>
  rename(geometry = x) |>
  mutate(geometry = geometry + c(-12, -3)) |>
  st_set_crs(2193)

@@

graphs <- mapply(
  get_lattice,
  # list(101, 150, 225, 110),
  list(101, 150, 110),
  # list(grid_pts, grid_pts, grid_pts, hex_grid_pts))
  list(grid_pts, grid_pts, hex_grid_pts))
# names(graphs) <- list("Rook's move", "Queen's move", "Knight's move", "Hex")
names(graphs) <- list("Rook's move", "Queen's move", "Hex")
```

@@

wrap_plots(ggplots, nrow = 1) & theme(
  plot.background = element_rect(fill = "black"),
  text = element_text(colour = "white")
)
```

### We went with hexagonal at ~100m spacing

@@

>>>>

##
![](fig-study-area-1.png){width="80%" fig-align="center"}

![](north-arrows.png){.absolute top=65 left=177 width="200" .fragment .fade-in-then-out}

![](fig-study-area-1.png){.absolute top=0 left=0 width="80%" fig-align="center" .fragment}

@@

get_graph_plot <- function(G, main, crs = 2193) {
  return(ggplot() +
    geom_sf(data = G |> get_graph_as_line_layer(crs = 2193),
            lwd = 1, colour = "grey") +
    geom_sf(data = G |> vertex_attr() |> as.data.frame() |> 
              st_as_sf(coords = 1:2, crs = crs), size = 12,
              colour = "#191919", fill = "grey", shape = 21) +
    coord_sf(xlim = c(-270, 270) + 1e6, 
             ylim = c(-270, 270) + 1e6, expand = FALSE) +
    ggtitle(main)) +
    theme(
      plot.background = element_rect(fill = "#191919"),
    )
}

@@

hex_grid_pts <- grid_pts |>
  st_bbox() |> 
  st_make_grid(square = FALSE, what = "centers", cellsize = 107.457) |>
  st_as_sf() |>
  rename(geometry = x) |>
  st_set_crs(2193)

@@

graphs <- mapply(
  get_lattice,
  list(101, 150, 110),
  list(grid_pts, grid_pts, hex_grid_pts))
names(graphs) <- list("Rook's move", "Queen's move", "Hex")
```

@@

wrap_plots(ggplots, nrow = 1) & theme(
  plot.background = element_rect(fill = "#191919"),
  text = element_text(colour = "white")
)
```

### We went with hexagonal at ~107m spacing

@@

![](betweenness.png){fig-align="center"}
